Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-06 paper/paper.tex

\subsection{Seed JS files\label{sec:seeds}}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy
    integration.\Mar{not clear what you mean}
\end{itemize}

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used to find projects with JS files\Mar{why the query is so specific?
  as per ``q=javascript-engine''? Need to be consistent to what you
  are saying an coherent to what you actually did.}. The query sorts
results in descending order in the number of stars\Mar{sorting is only
  relevant if you set a limit on the number of projects you will
  analyze. What limit is that?}. The resulting list includes a total
of \Fix{XX} projects. A total of \Fix{...}  projects remained after
removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
the JS sources we considered for each of these selected
projects..\Mar{identify the sources assoc. with the four analyzed
  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

>>>>

\subsection{Seed JS files\label{sec:seeds}}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item It does not use external libraries 
\end{itemize}

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used to find javascript engines projects defined by the keyword "javascript-engine". 
The resulting list includes a total of 33 projects.
A total of \Fix{...}  projects remained after
removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
the JS sources we considered for each of these selected
projects..\Mar{identify the sources assoc. with the four analyzed
  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}
